---
title: Generate Reproducible & Live HTML and PDF Conference Posters Using RMarkdown
author:
  - name: Chengcheng Xu
    affil: 1
  - name: Tuyen Bich Duong
    affil: 1
  - name: Fanxing Yu
    affil: 1
  - name: Wenxin Zhou
    affil: 1
affiliation:
  - num: 1
    address: Department of Statistics, UCLA
# - num: 2
#   address: Some other affiliation
column_numbers: 3
font_family: Helvetica
primary_colour: "#2774AE"
secondary_colour: "#FFD100"
accent_colour: "#003B5C"
affiliation_textcol: "#FFD100"
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoleft_name: http&#58;//www.firststar.org/wp-content/uploads/2015/02/ucla1.jpg
## https://ev0awwmgj4-flywheel.netdna-ssl.com/wp-content/uploads/images/products/products-University-of-CA-Los-Angeles-Seal.jpg
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

Welcome to `posterdown` ! This is my attempt to provide a semi-smooth workflow for those who wish to take their R Markdown skills to the conference world. Most features from R Markdown are available in this package such as Markdown section notation, figure captioning, and even citations like this one [@R-rmarkdown]. The rest of this example poster will show how you can insert typical conference poster features into your own document. 

# Image
```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
knitr::include_graphics("https://ca-times.brightspotcdn.com/dims4/default/4d3b462/2147483647/strip/true/crop/1000x650+0+0/resize/840x546!/quality/90/?url=https%3A%2F%2Fca-times.brightspotcdn.com%2F1a%2Fce%2F1f17cb25894c5c06fcb15d4c0ce8%2Fla-sp-sn-ucla-football-defensive-line-20140813-001")
```

## Objectives

1. Easy to use reproducible poster design. 
2. Integration with R Markdown.
3. Easy transition from `posterdown` to `pagedown` report or manuscript documents [@R-pagedown].

# Methods

This package uses the same workflow approach as the R Markdown you know and love. Basically it goes from RMarkdown > Knitr > Markdown > Pandoc > HTML/CSS > PDF. You can even use the bibliography the same way [@R-posterdown].

# Results

Let's see the results from a SVM model!

```{r mytable, out.width='80%', warning=FALSE}
library(mvtnorm)
library(e1071)

# generation of data
# try making different data sets
xa <- rmvnorm(10,mean = c(0,0), sigma = diag(2))
xb <- rmvnorm(10, mean = c(2,2), sigma = diag(2))
x <- rbind(xa, xb)
df <- data.frame(x, y =c(rep('-1', 10), rep(1, 10)))
knitr::kable(df, caption = 'Table of our data',align = 'c',"html")
plot(df$X1,df$X2, col = df$y, pch = 19, asp = 1) # create a plot of the mixture

```



```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
# the SVM model. Try changing kernel type between linear/radial, and using different values of gamma and cost
model <- svm(y ~ . , data = df, scale = FALSE, kernel = "radial", gamma = 1, cost = 1)

# The code to plot the decision boundary
## used to create a grid of red/black points 
x1range <- seq(-3,4.2,by = 0.1); x2range <- seq(-2,3,by = 0.1)
xgrid <- expand.grid(X1 = x1range, X2 = x2range)
ygrid <- predict(model, xgrid, decision.values = TRUE)
# extract svm's decision values for each point, which will be used to draw contour lines
decision_vals = attributes(ygrid)$decision
plot(xgrid, col = as.numeric(ygrid), pch = 20, cex = .2) # plot the grid of points colored by the decision
points(df$X1, df$X2, col = df$y, pch = 19) # add the points in the original data
## add some contour lines
contour(x1range, x2range, matrix(decision_vals, nrow = length(x1range)), level = 0, add = TRUE, lwd = 2)
contour(x1range, x2range, matrix(decision_vals, nrow = length(x1range)), level = 0.5, add = TRUE, col = "black")
contour(x1range, x2range, matrix(decision_vals, nrow = length(x1range)), level = -0.5, add = TRUE, col = "red")
```

# Next Steps

Aliquam sed faucibus risus, quis efficitur erat. Vestibulum semper mauris quis tempus eleifend. Aliquam sagittis dictum ipsum, quis viverra ligula eleifend ut. Curabitur sagittis vitae arcu eget faucibus. In non elementum felis. Duis et aliquam nunc. Nunc pulvinar sapien nunc, vel pretium nisi efficitur in. Fusce fringilla maximus leo et maximus. Fusce at ligula laoreet, iaculis mi at, auctor odio. Praesent sed elementum justo. Aenean consectetur risus rhoncus tincidunt efficitur. Praesent dictum mauris at diam maximus maximus [@R-posterdown].

# Conclusion

Try `posterdown` out! Hopefully you like it!

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
