---
title: Support vector machine implemented by RMarkdown 
author:
  - name: Chengcheng Xu
    affil: 1
  - name: Tuyen Bich Duong
    affil: 1
  - name: Fanxing Yu
    affil: 1
  - name: Wenxin Zhou
    affil: 1
affiliation:
  - num: 1
    address: Department of Statistics, UCLA
# - num: 2
#   address: Some other affiliation
column_numbers: 3
font_family: Helvetica
primary_colour: "#2774AE"
secondary_colour: "#FFD100"
accent_colour: "#003B5C"
affiliation_textcol: "#FFD100"
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoleft_name: http&#58;//www.firststar.org/wp-content/uploads/2015/02/ucla1.jpg
## https://ev0awwmgj4-flywheel.netdna-ssl.com/wp-content/uploads/images/products/products-University-of-CA-Los-Angeles-Seal.jpg
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

Welcome to `Team 2 Posterdown`. In this poster, we demonstrate a simple example of how to use **Support vector machine** to decide a boundary between two groups of data, including the used dataset, R codes, and some graphical results.

# Image
```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
knitr::include_graphics("https://ca-times.brightspotcdn.com/dims4/default/4d3b462/2147483647/strip/true/crop/1000x650+0+0/resize/840x546!/quality/90/?url=https%3A%2F%2Fca-times.brightspotcdn.com%2F1a%2Fce%2F1f17cb25894c5c06fcb15d4c0ce8%2Fla-sp-sn-ucla-football-defensive-line-20140813-001")
```

## Objectives

1. Introduction to Support vector machine method.
2. Implematation of R codes and functions for support vector machine.
3. Data visualization.

# Methods

Using `svm()` function in R to create the boundary for a given data.
Gaphing data and the resuts by R base plot and contour functions.

# Results

Let's see the results from a SVM model!

```{r mytable, out.width='80%', warning=FALSE}
library(mvtnorm)
library(e1071)

# generation of data
# try making different data sets
xa <- rmvnorm(10,mean = c(0,0), sigma = diag(2))
xb <- rmvnorm(10, mean = c(2,2), sigma = diag(2))
x <- rbind(xa, xb)
df <- data.frame(x, y =c(rep('-1', 10), rep(1, 10)))
knitr::kable(df, caption = 'Table of our data',align = 'c',"html")
plot(df$X1,df$X2, col = df$y, pch = 19, asp = 1) # create a plot of the mixture

```



```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
# the SVM model. Try changing kernel type between linear/radial, and using different values of gamma and cost
model <- svm(y ~ . , data = df, scale = FALSE, kernel = "radial", gamma = 1, cost = 1)

# The code to plot the decision boundary
## used to create a grid of red/black points 
x1range <- seq(-3,4.2,by = 0.1); x2range <- seq(-2,3,by = 0.1)
xgrid <- expand.grid(X1 = x1range, X2 = x2range)
ygrid <- predict(model, xgrid, decision.values = TRUE)
# extract svm's decision values for each point, which will be used to draw contour lines
decision_vals = attributes(ygrid)$decision
plot(xgrid, col = as.numeric(ygrid), pch = 20, cex = .2) # plot the grid of points colored by the decision
points(df$X1, df$X2, col = df$y, pch = 19) # add the points in the original data
## add some contour lines
contour(x1range, x2range, matrix(decision_vals, nrow = length(x1range)), level = 0, add = TRUE, lwd = 2)
contour(x1range, x2range, matrix(decision_vals, nrow = length(x1range)), level = 0.5, add = TRUE, col = "black")
contour(x1range, x2range, matrix(decision_vals, nrow = length(x1range)), level = -0.5, add = TRUE, col = "red")
```

# Next Steps

Aliquam sed faucibus risus, quis efficitur erat. Vestibulum semper mauris quis tempus eleifend. Aliquam sagittis dictum ipsum, quis viverra ligula eleifend ut. Curabitur sagittis vitae arcu eget faucibus. In non elementum felis. Duis et aliquam nunc. Nunc pulvinar sapien nunc, vel pretium nisi efficitur in. Fusce fringilla maximus leo et maximus. Fusce at ligula laoreet, iaculis mi at, auctor odio. Praesent sed elementum justo. Aenean consectetur risus rhoncus tincidunt efficitur. Praesent dictum mauris at diam maximus maximus [@R-posterdown].

# Conclusion

**Support vector machine** is one of the powerful supervised learning models that can analyzed data used for classification and regression analysis. 

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
